%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Younes BOUCHBOUK} \\ \vspace{1pt}
    Software Engineer | Go/React Specialist | Building Scalable Cloud-Native Systems \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faMapMarker\ Casablanca, Morocco \hspace{4pt}
    \small \raisebox{-0.1\height}\faPhone\ +212-708204919 ~  \hspace{4pt} \href{mailto:younesbouchbouk.py@gmail.com}
    {\raisebox{-0.2\height}\faEnvelope\  \underline{younesbouchbouk.py@gmail.com}} ~  \\ \vspace{2pt}
    \href{https://www.linkedin.com/in/younes-bouchbouk/}{\raisebox{-0.2\height}\faLinkedin\ \underline{/younes-bouchbouk}}  ~
    \href{https://github.com/YounesBouchbouk}{\raisebox{-0.2\height}\faGithub\ \underline{/YounesBouchbouk}} ~
    \href{https://younesdev.com}{\raisebox{-0.2\height}\faGlobe\ \underline{younesdev.com}}
    \vspace{-8pt}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  
\resumeSubHeadingListStart
   \resumeSubheading
      {OmniLab by 21Factory (Startup)}{Jul 2025 -- Present}
      {Mid-level Software Engineer, Full-time}{Casablanca, MA}
      \resumeItemListStart
        \resumeItem{Domain expert for \textbf{Event Booking} and \textbf{SmartLink} microservices, owning end-to-end architecture and delivery.}
        \resumeItem{Built immersive AR experiences with \textbf{Three.js}, increasing user engagement by 35\% on the gamification SaaS platform.}
        \resumeItem{Designed and implemented \textbf{Golang microservices} following \textbf{DDD} and \textbf{Hexagonal/Clean Architecture} patterns.}
        \resumeItem{Built efficient APIs with \textbf{gRPC} and \textbf{Google AIP} standards for inter-service communication.}
        \resumeItem{Integrated production-grade observability using \textbf{Datadog}, \textbf{OpenTelemetry}, and \textbf{ClickStack/ClickHouse}.}
        \resumeItem{Deployed and managed services on \textbf{Kubernetes} with \textbf{Docker} and \textbf{GitLab CI/CD} pipelines.}
        \resumeItem{Applied \textbf{TDD} and implemented resilience patterns (Circuit Breaker) to ensure high reliability.}
      \resumeItemListEnd
      
   \resumeSubSubheading
      {Software Engineer, Full-time}{Sep 2024 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{Contributed to the same platform, delivering reliable backend services and user-facing features.}
        \resumeItem{Fixed production issues and improved performance, reducing API latency by 40\%.}
        \resumeItem{Technologies: Go, gRPC, Kubernetes, Docker, Datadog, React.js, Next.js, Three.js, TDD.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
    \vspace{-8pt}
    
\resumeSubHeadingListStart
    \resumeSubheading
      {Oracle Corporation}{Jan -- Jun 2024}
      {Research Assistant (Back-End), Internship}{Casablanca, MA}
      \resumeItemListStart
        \resumeItem{Improved and automated testing processes for \textbf{Graal Cloud Native Guides} (graal.cloud/gcn/guides).}
        \resumeItem{Developed new features and fixed bugs for a \textbf{notebook-based data science platform} (Oracle Labs Data Studio).}
        \resumeItem{Worked on \textbf{Jupyter integration}: themes, system file access, and embedding Jupyter via iframes.}
        \resumeItem{Technologies: Java Spring, TypeScript, Python, Jupyter Lab, Docker, Kubernetes.}
      \resumeItemListEnd
\resumeSubHeadingListEnd
    \vspace{-8pt}
    
\resumeSubHeadingListStart
    \resumeSubheading
      {ISPApp (Startup)}{Aug 2022 -- Jul 2023}
      {Full-Stack Developer, Freelance}{Dover, USA (Remote)}
      \resumeItemListStart
        \resumeItem{Developed a user-centric dashboard that streamlined router management for ISPs.}
        \resumeItem{Integrated \textbf{Plotly} for real-time visualization of network metrics (ping, TCP, interfaces, wireless APs).}
        \resumeItem{Technologies: React.js, Next.js, Node.js, TailwindCSS, Plotly.}
    \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Circuit Breaker Pattern Implementation} $|$ \emph{Golang, Microservices, Resilience Patterns}}{}
          \resumeItemListStart
            \resumeItem{Built a production-grade Circuit Breaker library in Go with Closed/Open/Half-Open state machine, thread-safe metrics, and configurable thresholds. Published as a technical blog post demonstrating microservices resilience patterns.}
          \resumeItemListEnd
          
          \vspace{-15pt}

    \resumeProjectHeading
          {\textbf{SENDIT: Full-Stack Delivery Network Application} $|$ \emph{React, Node.js, MongoDB, Neo4j}}{}
          \resumeItemListStart
            \resumeItem{Full-stack web application using MERN stack with Neo4j for shortest path optimization between cities in Morocco. Supports multi-hop deliveries across multiple delivery services.}
          \resumeItemListEnd
          
          \vspace{-15pt}
          
      \resumeProjectHeading
          {\textbf{ISPApp Network Management Dashboard} $|$ \emph{Next.js, Node.js, TailwindCSS, Plotly, Leaflet}}{}
          \resumeItemListStart
             \resumeItem{Implemented a robust router monitoring system with real-time graphs (ping, TCP, interfaces, wireless APs) using Plotly and interactive maps with Leaflet for network equipment visualization.}
          \resumeItemListEnd
          \vspace{-15pt}

    
    \resumeProjectHeading
          {\textbf{Person Re-identification System} $|$ \emph{Python, OpenCV, YOLOv4, Machine Learning}}{}
          \resumeItemListStart
            \resumeItem{Desktop application for detecting and tracking individuals using YOLO v4 for object detection and SIFT/ORB algorithms for feature extraction and re-identification across multiple camera feeds.}
          \resumeItemListEnd 
 
\vspace{-15pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Institute Of Posts And Telecommunications (INPT)}{Sep 2022 -- Jul 2024}
      {Engineer Degree: Data and Software Engineering}{Rabat, MA}
    
      \resumeSubheading
      {Polydisciplinary Faculty of Taroudant (FP)}{Sep 2021 -- Jul 2022}
      {Professional License: Computer Science}{Taroudant, MA}

      \resumeSubheading
      {Superior School of Technology (EST)}{Sep 2019 -- Jul 2021}
      {Technical University Degree: Computer Science}{Safi, MA}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Golang, JavaScript, TypeScript, Java, Python, Bash.} \\
     \textbf{Backend \& Architecture}{: Microservices, DDD, Hexagonal/Clean Architecture, gRPC, Google AIP, REST APIs.} \\
     \textbf{Observability \& Monitoring}{: Datadog, OpenTelemetry, ClickStack, ClickHouse.} \\
     \textbf{DevOps \& Cloud}{: Docker, Kubernetes, GitLab CI/CD, AWS.} \\
     \textbf{Frontend}{: React.js, Next.js, Three.js, TailwindCSS.} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, MySQL, Redis.} \\
     \textbf{Tools \& Practices}{: Git, TDD, Circuit Breaker Pattern, VS Code, Cursor, Linux.} \\
     }}
 \end{itemize}
 \vspace{-16pt}


\end{document}
